A pair of co-moving, Sun-like stars with different chemical abundances:\\ a possible signature of copious rocky accretion (needs work)

### 2017-04-26 paper/ms.tex
paragraph on inhomogeneity

% define macros for text
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\gaia}{\project{Gaia}}
\newcommand{\rave}{\project{\acronym{RAVE}}}
\newcommand{\apogee}{\project{\acronym{APOGEE}}}
\newcommand{\tmass}{\project{\acronym{2MASS}}}
\newcommand{\documentname}{Article}
\newcommand{\sectionname}{Section}
\newcommand{\figname}{Figure}
\newcommand{\eqname}{Equation}
\newcommand{\dr}{\acronym{DR1}}
\newcommand{\tgas}{\acronym{TGAS}}
\newcommand{\etal}{\textit{et al}.}
\newcommand*\elem[1]{\ensuremath{\mathrm{#1}}}
\newcommand*\elemH[1]{\ensuremath{[\mathrm{#1}/\elem{H}]}}
\newcommand{\sunanalog}{\text{HD 240429}}
\newcommand{\bizarreone}{\text{HD 240430}}

@@

Surface lithium abundance in a sun-like star such as \sunanalog\ decreases with its age
due to mixing induced by convection or rotation which brings lithium
into the interior ($T>2.5 \times 10^{6}$~K)
where it will be destroyed by proton capture burning.
Thus, surface lithium abundance is an indicator of stellar ages.
The $\elem{Li}$ abundance of $2.25$ for \sunanalog\ implies an age of $\lesssim 1$~Gyr
according to the theoretical models tuned to explain the solar lithium abundance
and rotational profile (\citealt{2005Sci...309.2189C}).
The lithium abundance of \bizarreone\ is still higher by $0.5$~dex
showing the largest difference among all measured elements.
Given the overall higher metal abundances and the peculiar abundance patterns in \bizarreone,
it is unclear, however, whether this higher $\elem{Li}$ abundance
means a younger age or something else.
For example, the presence of $\elem{Li}$-rich red giant stars has been attributed
to the engulfment of substellar companions such as gas giant planets or brown dwarfs
which may replenish $\elem{Li}$ (\citealt{Casey:2016aa}).
We come back to the $\elem{Li}$ difference later in our discussion.

@@

% binary-single and binary-binary exchange
Two stars unrelated at birth may end up in a binary system via binary-single scattering event
that results in an exchange of binary member.
In order to estimate the rate at which any binary-single
event will produce a wide binary system such as \sunanalog\ and \bizarreone,
we may consider the rate at which this wide binary will scatter with a field star to
result in an exchange reaction.
The cross-section of exchange scattering for a binary with semi-major axis $a$ is
\begin{eqnarray}
  \sigma_\mathrm{ex} = \frac{640}{81} \pi a^{2} \frac{1}{v^6}
\end{eqnarray}
where $v$ is the incoming velocity $v_i$ in units of critical velocity $v_c$ defined as
\begin{eqnarray}
  v_c^2 = G \frac{m_1 m_2 (m_1 + m_2 + m_3)}{m_3 (m_1 + m_2)} \frac{1}{a}
\end{eqnarray}
when $v \gg 1$ using the impulse approximation (\citealt{Hut:1983aa,Hut:1983ab}),
which is appropriate for wide binaries scattering with field (disk) stars.
If we assume that field stars are made of solar mass stars
with constant number density $n=1$~pc$^{-3}$, and the incoming velocity of field stars
is $10$~km\,s$^{-1}$, a lower limit to the velocity dispersions of disk
stars in any direction, the rate of exchange scattering is
\begin{eqnarray}
  n \sigma_\mathrm{ex} v_i = 6.82\times 10^{-8}\,\mathrm{Gyr}^{-1}
  \frac{n}{\mathrm{pc}^3} \frac{\mathrm{pc}}{a} \left(\frac{10~\mathrm{km}\,\mathrm{s}^{-1}}{v_i}\right)^5
\end{eqnarray}
low enough to be negligible.

@@

None of the above scenarios is quite satisfactory as it offers no
insight on the peculiarity in abundances of HD 30 (see \sectionname~{\ref{sec:data}).

@@

% inhomogeneity in star formation
It may be that the two stars are born at the same time from the same cloud, but
there is inhomogeneity. Highly doubtful based on
- Brewer et al. binaries that seem identical.
- other?

>>>>

% define macros for text
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\gaia}{\project{Gaia}}
\newcommand{\rave}{\project{\acronym{RAVE}}}
\newcommand{\apogee}{\project{\acronym{APOGEE}}}
\newcommand{\tmass}{\project{\acronym{2MASS}}}
\newcommand{\documentname}{Article}
\newcommand{\sectionname}{Section}
\newcommand{\figname}{Figure}
\newcommand{\eqname}{Equation}
\newcommand{\dr}{\acronym{DR1}}
\newcommand{\tgas}{\acronym{TGAS}}
\newcommand{\etal}{\textit{et al}.}
\newcommand*\elem[1]{\ensuremath{\mathrm{#1}}}
\newcommand*\elemH[1]{\ensuremath{[\mathrm{#1}/\elem{H}]}}
\newcommand*{\feh}{\ensuremath{\elemH{Fe}}}
\newcommand{\sunanalog}{\text{HD 240429}}
\newcommand{\bizarreone}{\text{HD 240430}}

@@

Surface lithium abundance in a sun-like star such as \sunanalog\ decreases with its age
due to mixing induced by convection or rotation which brings lithium
into the interior ($T>2.5 \times 10^{6}$~K)
where it will be destroyed by proton capture burning.
Thus, surface lithium abundance is an indicator of stellar ages.
The $\elem{Li}$ abundance of $2.25$ for \sunanalog\ implies an age of $\lesssim 1$~Gyr
according to the theoretical models tuned to explain the solar lithium abundance
and rotational profile (\citealt{2005Sci...309.2189C}).
The lithium abundance of \bizarreone\ is still higher by $0.5$~dex
showing the largest difference among all measured elements.
This translates to $\sim 500$~Myr difference in age.
Given the overall higher metal abundances and the peculiar abundance patterns in \bizarreone,
it is unclear, however, whether this higher $\elem{Li}$ abundance
means a younger age or something else.
For example, the presence of $\elem{Li}$-rich red giant stars has been attributed
to the engulfment of substellar companions such as gas giant planets or brown dwarfs
which may replenish $\elem{Li}$ (\citealt{Casey:2016aa}).
We come back to the $\elem{Li}$ difference later in our discussion.

@@

% binary-single and binary-binary exchange
Two stars unrelated at birth may end up in a binary system via binary-single scattering event
that results in an exchange of binary member.
In order to estimate the rate at which any binary-single
event will produce a wide binary system such as \sunanalog\ and \bizarreone,
we may consider the rate at which this wide binary will scatter with a field star to
result in an exchange reaction.
The cross-section of exchange scattering for a binary with semi-major axis $a$ is
\begin{eqnarray}
  \sigma_\mathrm{ex} = \frac{640}{81} \pi a^{2} \frac{1}{v^6}
\end{eqnarray}
where $v$ is the incoming velocity $v_i$ in units of critical velocity $v_c$ defined as
\begin{eqnarray}
  v_c^2 = G \frac{m_1 m_2 (m_1 + m_2 + m_3)}{m_3 (m_1 + m_2)} \frac{1}{a}
\end{eqnarray}
when $v \gg 1$ using the impulse approximation (\citealt{Hut:1983aa,Hut:1983ab}),
which is appropriate for wide binaries scattering with field (disk) stars.
If we assume that field stars are made of solar mass stars
with constant number density $n=1$~pc$^{-3}$, and the incoming velocity of field stars
is $10$~km\,s$^{-1}$, a lower limit to the velocity dispersions of disk
stars in any direction, the rate of exchange scattering is
\begin{eqnarray}
  n \sigma_\mathrm{ex} v_i = 6.82\times 10^{-8}\,\mathrm{Gyr}^{-1}
  \frac{n}{\mathrm{pc}^3} \frac{\mathrm{pc}}{a} \left(\frac{10~\mathrm{km}\,\mathrm{s}^{-1}}{v_i}\right)^5
\end{eqnarray}
low enough to be negligible.
Because the exchange scattering cross section steeply depends on the incoming velocity
relative to the critical velocity (of the order of orbital velocity of the binary),
the rate of exchange scattering with a star within the same star forming region
may be much larger.
However, even in such scenario, the age difference of $\sim 500$~Myr is too large
for two stars of the same star forming region.

@@

None of the above scenarios is satisfactory as it offers no
insight on the peculiarity in abundances of HD 30 (see \sectionname~{\ref{sec:data}).

@@

% inhomogeneity in star formation
It may be that the two stars are born at the same time from the same cloud, but
there is inhomogeneity within the cloud.
However, there is already ample amount of evidence against such scenario.
First, none of the other seven similar wide binaries examined in \citealt{2016ApJS..225...32B}
show the same level differences in abundances although there is generally
a larger spread in $\elem{C}$, $\elem{N}$ and $\elem{O}$, and some pairs show
a large as $\approx 0.15$~dex difference in particular elements.
The median and maximum \feh\ difference between component stars in the other seven pairs
is $0.02$~dex and $0.09$~dex, respectively.
This is consistent with the findings of \citealt{Desidera:2004aa} who examined 23 wide bianries
of late F to K dwarfs, and found most pairs show difference in \feh\ less than $0.02$~dex
and none larger than $0.07$~dex.

% summarize other pair studies in detailed chemical abundance here
